### 2019-08-12 Thesis/pages/design.tex
Changes; - Added further discussion to the report
Changes; - Checked through the writing up until the Implementation section

This chapter will discuss and overview of the proposed designs for elements required to answer the research questions. Alternative designs are explained when relevant and design choices are justified

@@

As each combined key in Trustwords is an exclusive-or of both sides public key (Figure \ref{fig:xor_trustwords} shows this process) the attack is target to a single pair of users and will require recomputation for every attack target. This will be considered when discussing the attack feasibility. Each pair is also split into a "Uncontrolled" and "Controlled" key. Uncontrolled is the reciever of the communication, and, thus, we cannot control their key. The Controlled key is the one we are attempting to impersonate, and it is assumed that we have the ability to replace the Controlled key with our malicious option. These descriptions will be the terminology used throughout the paper. However, it should also be considered that the uncontrolled and controlled can be swapped around with the ability to compute both directions. Thus, resulting in the possibility to intercept both directions of communication. This, however, will require performing the attack separately for both directions.

@@

Figure \ref{fig:nearMatch} shows the process of generating a sub section of the combinations. A list of each words matches are generated and then the total number of permutations are generated overall.

@@

To generate an actual list of fingerprints to search for, the near collision words are converted back into hexadecimal and XORed with the uncontrolled key. The provides the impersonated key that will produce the desired combined near-collision. Completing this for all of the near-collision permutations will produce a list of fingerprints that can be inserted into a tool designed to hash keys and search for targets. This aspect of using a large list to search for keys massively reduces the complexity of the search.

In summary the, attack steps are:

@@

    \item Use list of similar keys in mass computation of keys to find near-collision keys.

@@

\section{Similarity metrics}
\label{sec:metrics}
One of the first requirements for the attack is quantifying "phonetic similarity". This section is looking to provide an answer for the Research Question \ref{goal:phoneticSimilarity}. There are many algorithms currently available to provide this functionality. This section will describe algorithms alongside the reasons they were selected for assessment later in the project.

\subsection{Soundex}
One of the earliest example of a phonetic algorithm is known as Soundex. It is one of the most famous algorithm due in part to its implementation into major database clients like MySQL\cite{mysql_soundex}, Oracle\cite{moved_2005} and PostgreSQL\cite{postgresql}. Originally designed for indexing names by phonetics alongside spelling mistakes due to transpositions in letters. Therefore, due to it being based on the phonetic features, it is highly suitable for this project's use-case.

@@

    \item \textbf{Poor precision.} Due to the previously discussed point of a small code space. \cite{patman2001soundex} re-iterates this point but in the context of name matching where Soundex's poor performance was demonstrated. Soundex only gained and overall accuracy 36.37\% when matching names within a provided database.
\end{enumerate}

@@

\subsection{Phonetic Vectors}
Phonetic Vectors is the unique addition to the chosen set. Created by Allison Parrish in 2017\cite{parrish2017poetic}, Phonetic vectors is as the name suggests the vectorization of a words phonetics. This allows a words phonetics to be represented in vector space.

@@

\subsection{Caverphone}
Another notable alternative solution is that of Caverphone that was designed in New Zealand. Caverphone as is the case with the vast majority of phonetic algorithms was designed for use with name matching. Caverphone was not chosen to similar reasons to that of MRA alongside its optimization for accents in location of New Zealand it was conceived in. Therefore, the low level of utilization alongside the unique design features that suggest it may not be suited for this application. This has, however, not be assessed empirically and thus would be a candidate for further work.

@@

The tool should take two keys as parameters (Uncontrolled/Controlled) and a chosen similarity metric and produce a list of target keys fingerprints. This list is then used as a search criteria when hashing a checking a large number of keys. In order to utilise the high parallel nature of the GPU to compute the hash of a large number of keys the tool will utilise a GPGPU (General-purpose computing on graphics processing units) framework. The chosen framework was OpenCL due to its support for the chosen language (C++) and platform (Linux). OpenCL allows the creation of code chunks refereed to as "kernels" to be executed concurrently, this will provide a massive speed increase compare to the sequential nature of the CPU. Technical details will be explained further in Chapter \ref{cha:Implementation}.

@@

\subsection{Metric performance}
\label{exp:metric}
In order to answer Research Question \ref{goal:bestMetrics} and reduce the number of metrics to asses in the later rounds, the performance of similarity metrics required comparison. The thinning out of metrics is required due to limited resources and, therefore, possible further work could involve repeating this work with a much more varied selection of metrics. As explained in a previous section (See Section \ref{sec:metrics}) the chosen metrics up for assessment are Soundex, Metaphone, NYSIIS, Levenshtein and Phonetic vectors.

@@

\newpage

@@

The final check to ensure the validity of results is a check for native English fluency. Having non-native English speakers complete the 
experiment has the possibility to introduce inconsistencies into the 
data and, therefore, needs to remain controlled. To achieve this a 
preliminary MTurk study will be run to ask users for their perceived 
English fluency on a scale of 1 (Basic Understanding) to 5 (Native). 
Workers with an answer of 5 will be provided with a 
Qualification\footnote{\url{https://blog.mturk.com/tutorial-understanding-requirements-and-qualifications-99a26069fba2}} 
that tags them as defining themselves as native speakers. This is then 
added as a prerequisite when running the experiment. This will insure 
only fully native speakers are being assessed. The possibility of the 
worker falsy stating their level of fluency has also been considered. 
However, as the worker does not know the purpose for this initial study,
thereby providing inaccurate results has no real valid motive for the 
worker.

\subsubsection{Statistical}
\textbf{TODO}

@@

The first consideration is the way the words are compared. Due to the channel of authentication being phone based the comparison of words will be a mixture of auditory and textual. This is because a user needs to match a words sound to the one displayed on their device. In the case of this experiment the users are asked to compare the sound of two word that are visually displayed to them. This visual aspect is the first point of contact between the participant and the question, followed by mental comparison of the phonetics of the word. Therefore, this initial visual contact has the potential to bias the results of the study. This has the potential to affect Levenshtein due to the matches never being more than one character different, therefore, resulting in very similar looking words. The alternative method of running this experiment is to get users to compare audio samples of words, this will force the user to compare just the phonetics of the words and not be influenced by the visual aspects of the pair. This, however, adds a substantial cost onto the operation of the study. Due to the aforementioned lack of resources the chosen design was decided as most feasible as it is a balance between cost and accuracy. Further work, therefore, could improve by producing more conclusive results on the performance of the metrics by implementing the more accurate but costly alternative.

@@

\subsection{Trustword Attacks}

@@

Certain keys have higher levels of near-collision possibilities than others due to how certain words are deemed similar by the chosen metric. Therefore, this presents the possibility to have keys with a very low number of similar matches. The distribution of these keys will be explained further in Chapter \ref{cha:Experiments}. Therefore, if random sets of words were chosen with no restraints there are attacks presented to the user that in a real setting would be infeasible in this context as they are close to a $2^{64}$ attack (4 Words * 16-bits). Therefore, the experiment will sample from a list of "vulnerable" keys. These are keys that have a number of combinations that allow an attack in a certain timeframe. Furthermore, certain levels of attacks are also simulated. Below are the list of possible attacks:

@@

However, this may not be applicable in this context due to the user being linearly fed an audio stream that they cannot skip to the start or end. We believe, however, that attention will also play a part in defining the most important areas of comparison as the hypothesis is that the users attention will be lower in the middle sections of comparison where it peak at the start and end. All these aspects will require empirical evidence to arrive at a conclusion. Therefore, this consideration will need to be made when assessing the results of the experiment.

These attacks are ascending in complexity. The timeframe for finding a match was decided as 7-days on with attack strengths of 1 GPU/day, 10 GPU/days and 100 GPU/days on a mid range GPU (AMD RX 480 was the example in experiments). Due to the long life time of PGP keys, 7 days was chosen as a reasonable length of attack, attackers can just leave the tool and have it compute potential keys for the target without any need for user engagement. This is also a maximum time, these attacks also include keys that have a shorter average computation time.

@@

\todo{Talk here about the sampling of vuln keys from keys harvested from PGP key servers.}

@@

Audio buttons clicks is the number of times the blue \textit{"Authenticate with partner over the phone"} button in Figure \ref{fig:expID}. If there are rounds without button clicks, this is a sign of non-attentive users. The design choice was made to keep this as a result filter, as preventing non-clicks would be a trivial task. This provides a way to detect and discard click-throughs\footnote{Workers that aim to complete the task as fast as possible, with no regard for the quality of responses}.

@@

\subsubsection{Statistical}
\textbf{TODO}

>>>>

This chapter will discuss and overview of the proposed designs for elements required to answer the research questions. Alternative solutions are explained when relevant alongside a justification of design choices.

@@

As each combined key in Trustwords is an exclusive-or of both sides' public key (Figure \ref{fig:xor_trustwords} shows this process) the attack is designed to target a single pair of users and will require recomputation for every attack target. This will be considered when discussing the attack feasibility. Each pair is also split into an "Uncontrolled" or "Controlled" key. Uncontrolled is the receiver of the communication, and, thus, we cannot control their key. The Controlled key is the one we are attempting to impersonate, and it is assumed that we have the ability to replace the Controlled key with our malicious option. These descriptions will be the terminology used throughout the paper. However, it should also be considered that the uncontrolled and controlled can be swapped around with the ability to compute both directions. Thus, resulting in the possibility to intercept both directions of communication. This, however, will require performing the attack separately for both directions.

@@

Figure \ref{fig:nearMatch} shows the process of generating a subsection of the combinations. A list of each words' matches is generated, followed by the generation of the total number of near-collision keys.

@@

In order to generate an actual list of fingerprints to search for, the near-collision words are converted back into hexadecimal and XORed with the uncontrolled key. This provides the impersonated key that will produce the desired Trustwords. Completing this for all of the near-collision permutations will produce a list of fingerprints that can be inserted into a tool designed to hash keys and search for targets. This aspect of using a large list to search for keys massively reduces the complexity of the search.

In summary, the attack steps are:

@@

    \item Use a list of similar keys in the mass computation of keys to find near-collision keys.

@@

\section{Similarity metrics}
\label{sec:metrics}
One of the first requirements for the attack is quantifying "phonetic similarity." This section is looking to provide an answer for Research Question \ref{goal:phoneticSimilarity}. There are many algorithms currently available to provide this functionality. This section will describe algorithms alongside the reasons they were selected for assessment later in the project.

\subsection{Soundex}
One of the earliest examples of a phonetic algorithm is known as Soundex. It is one of the most famous algorithm due in part to its implementation into major database clients like MySQL\cite{mysql_soundex}, Oracle\cite{moved_2005} and PostgreSQL\cite{postgresql}. Originally designed for indexing names by phonetics alongside spelling mistakes due to transpositions in letters. Therefore, due to it being based on the phonetic features, it is highly suitable for this project's use-case.

@@

    \item \textbf{Poor precision.} Due to the previously discussed point of a small code space. \cite{patman2001soundex} re-iterates this point but in the context of name matching where Soundex's poor performance was demonstrated. Soundex only gained and overall accuracy of 36.37\% when matching names within a provided database.
\end{enumerate}

@@

\subsection{Phonetic Vectors}
Phonetic Vectors is the unique addition to the chosen set. Created by Allison Parrish in 2017\cite{parrish2017poetic}, Phonetic vectors is as the name suggests the vectorization of a words phonetics. This phonetical representation in vector space.

@@

\subsection{Caverphone}
Another notable alternative solution is that of Caverphone that was designed in New Zealand. Caverphone as is the case with the vast majority of phonetic algorithms was designed for use with name matching. Caverphone was not chosen to similar reasons to that of MRA alongside its optimization for the New Zealand accent. Therefore, the low level of utilization alongside the unique design features that suggests it may not be suited for this application. This has, however, not be assessed empirically and thus would be a candidate for further work.

@@

The tool should take two keys as parameters (Uncontrolled/Controlled) and a chosen similarity metric and produce a list of target keys fingerprints. This list is then used as a search criteria when hashing a checking a large number of keys. In order to utilise the high parallel nature of the GPU to compute the hash of a large number of keys the tool will utilise a GPGPU (General-purpose computing on graphics processing units) framework. The chosen framework was OpenCL due to its support for the chosen language (C++) and platform (Linux). OpenCL allows the creation of code chunks referred to as "kernels" to be executed concurrently, this will provide a massive speed increase compare to the sequential nature of the CPU. Technical details will be explained further in Chapter \ref{cha:Implementation}.

@@

\subsection{Metric performance}
\label{exp:metric}
In order to answer Research Question \ref{goal:bestMetrics} and reduce the number of metrics to assess in the later rounds, the performance of similarity metrics required comparison. The thinning out of metrics is required due to limited resources and, therefore, possible further work could involve repeating this work with a much more varied selection of metrics. As explained in a previous section (See Section \ref{sec:metrics}) the chosen metrics up for assessment are Soundex, Metaphone, NYSIIS, Levenshtein and Phonetic vectors.

@@

\todo{Link the less than 100,000 point to experiment data}

@@

The final check to ensure the validity of results is a check for native English fluency. Having non-native English speakers complete the 
experiment has the possibility to introduce inconsistencies into the 
data and, therefore, needs to remain controlled. To achieve this a 
preliminary MTurk study will be run to ask users for their perceived 
English fluency on a scale of 1 (Basic Understanding) to 5 (Native). 
Workers with an answer of 5 will be provided with a 
Qualification\footnote{\url{https://blog.mturk.com/tutorial-understanding-requirements-and-qualifications-99a26069fba2}} 
that tags them as defining themselves as native speakers. This is then 
added as a prerequisite when running the experiment. This will insure 
only fully native speakers are being assessed. The possibility of the 
worker falsely stating their level of fluency has also been considered. 
However, as the worker does not know the purpose for this initial study,
thereby providing inaccurate results has no real valid motive for the 
worker.

@@

The first consideration is the way the words are compared. Due to the channel of authentication being phone based the comparison of words will be a mixture of auditory and textual. This is because a user needs to match a words sound to the one displayed on their device. In the case of this experiment the users are asked to compare the sound of two word that are visually displayed to them.

This visual aspect is the first point of contact between the participant and the question, followed by mental comparison of the phonetics of the word. Therefore, this initial visual contact has the potential to bias the results of the study. Levenshtein has the potential to be most affected by this due to the matches never being more than one character different, therefore, resulting in very similar looking words. The alternative method of running this experiment is to get users to compare audio samples of words, this will force the user to compare just the phonetics of the words and not be influenced by the visual aspects of the pair. This, however, adds a substantial cost onto the operation of the study. Due to the aforementioned lack of resources the chosen design was decided as most feasible as it is a balance between cost and accuracy. Further work, therefore, could improve by producing more conclusive results on the performance of the metrics by implementing the more accurate but costly alternative.

@@

\subsection{Trustword Attacks}
\label{sec:exp2_design}

@@

Certain keys have higher levels of near-collision possibilities than others due to how certain words are deemed similar by the chosen metric. Therefore, this presents the possibility to have keys with a very low number of similar matches. The distribution of these keys will be explained further in Chapter \ref{cha:Experiments}. Therefore, if random sets of words were chosen with no restraints there are attacks presented to the user that in a real setting would be infeasible as they are close to a $2^{64}$ attack (4 Words * 16-bits). Therefore, the experiment will sample from a list of "vulnerable" keys. These are keys that have a number of combinations that allow an attack in a certain timeframe. Furthermore, certain levels of attacks are also simulated. Below are the list of possible attacks:

@@

However, this may not be applicable in this context due to the user being linearly fed an audio stream that they cannot skip to the start or end. We believe, however, that attention will also play a part in defining the most important areas of comparison. The hypothesis is that the users attention will be lower in the middle sections of comparison where it peak at the start and end. All these aspects will require empirical evidence to arrive at a conclusion. Therefore, this consideration will need to be made when assessing the results of the experiment.

These attacks are ascending in complexity. The timeframe for finding a match was decided as 7-days with attack strengths of 1 GPU/day, 10 GPU/days and 100 GPU/days on a mid range GPU (AMD RX 480 was the example in experiments). Due to the long life time of PGP keys, 7 days was chosen as a reasonable length of attack, attackers can just leave the tool and have it compute potential keys for the target without any need for user engagement. This is also a maximum time, these attacks also include keys that have a shorter average computation time.

@@

@@

Audio buttons clicks is the number of times the blue \textit{"Authenticate with partner over the phone"} button in Figure \ref{fig:expID} is clicked. If there are rounds without button clicks, this is a sign of non-attentiveness. The design choice was made to keep this as a result filter, as preventing non-clicks would be a trivial task. This provides a way to detect and discard click-throughs\footnote{Workers that aim to complete the task as fast as possible, with no regard for the quality of responses}.

@@

### 2019-08-12 Thesis/pages/experiments.tex
Changes; - Checked through the writing up until the Implementation section

\begin{table}[h!]
    \centering
    \begin{tabular}{|l|l|l|}
        \hline
        Metric & Average Rating  & $\sigma$\\
        \hline
        Leven     & 3.66  & 1.15\\
        NYSIIS    & 2.92 & 1.31\\
        Metaphone & 2.56 & 1.32\\
        Phonetic Vec & 2.50 & 1.35\\
        Soundex & 2.08 & 1.12 \\
        \hline
        Random  & 1.16 & 0.46\\
        \hline
    \end{tabular}
    \caption{Average metric performance}
    \label{tab:exp1_results}
\end{table}

@@

\subsection{Limitations}

\textbf{TODO: } Reference back to the decisions made in the design section.

Therefore, even with the discussed issues, the aim of the experiment was to promptly reduce the number of metrics for use later in the project due to a lack of project resources.

This experiment, therefore, has achieved that goal of providing three metrics for the subsequent experiment while balancing between accuracy and expenditure. Further work could aim to reproduce this study with the proposed audio based design.

@@

\section{Experiment 2 - Simulated attacks}
\label{sec:exp2}
% Demographic
% Results

@@

As previously mentioned, the set of recruited participants are more highly educated than the general population. This combined with the low average age contributes to an inevitable bias being introduced into the data. An assumption can be made that higher education leads to more skillful interaction with computer based systems, this, therefore, with the previous assumption in mind results in the results of this experiment being a best case scenario as the attacks would be expected to be more successful with less able users. This, however, requires further research and possible empirical data to determine the validity of the assumption.

\subsection*{Limitations}
During this study the main task was to perform the authentication ceremony a large number of times. In the real-world the ceremony is a secondary task due to it not strictly being required. This alongside the potential for users to downplay the possibility of attack leads to the conclusion that these results have limited applicability in a real-world setting. The assumption is that these results display the success rate for extremely attentive user where they will make sure to double check with their participant and not just aim to complete the task as quickly as possible. This, therefore, means in a real-world setting the success rates could be even higher.

\todo{Include email example of user assuming error over attack}.

\subsection{Comparison to alternative literature}
This section will aim to compare the results of the experiment to similar literature.

Work by Kainda \textit{et al.}\cite{kainda2009usability} (previous discussed in Chapter \ref{cha:LiteratureReview}) is the most comparable to this experiment. They were the only study to use exactly 4 words, but differed on the size of dictionary (1024 words) and how a near-match was calculated. Near-matches were a difference in a single word, but without the consideration for similarity, this is the unique aspect considered with this experiment.

However, with those aspect in mind Words received an overall success rating of 3.3\%, considerably lower than that of this study. The results presented in this experiment in the worst case presented almost 3 times as many successful attacks.

Other relevant work by Dechand \textit{el al.}\cite{dechand2016empirical} also discussed in Chapter \ref{cha:LiteratureReview} assess the success rate of attacks on words. This is less similar to the experiment as 14 words per attack were assessed with each participant, where the comparison was performed visually. However, the success for the PGP Word list was 8.78\%. As 10/14 words were kept static more comparable to comparable the results to the highest attack strength ``2 static''. Therefore, the results presented in this section are substantially higher than this paper, where again the success rate is almost 3 times higher.

The final relevant paper to compare is that of Tan \textit{et al.}. This paper had the highest number of words assessed with 16 overall. With it assessing the same wordlist and attack strength as the work by Dechand \textit{et al.}. The attack success was 14\% overall, this again compared to the highest attack assessed in the experiment results in a sizeable difference between the attack successes.

In conclusion, all similar literature had much lower attack success rates that the results presented in this experiment. With all papers using similarly designed words lists it highly suggests that the deficiencies in Trustwords are the cause for the substantial increase in attack success. Furthermore, the consideration for similarity of words that the other papers have not considered could have also resulted in the higher attack success rates.

@@

\begin{table}[!h]
    \centering
    \begin{tabular}{|lllll|}
        \hline
        \textbf{Metric} & \textbf{Attack Type} & \textbf{Mean permuations} & \textbf{$\sigma$} & \textbf{Compute Time} \\
        \hline
        NYSIIS &&&& \\
        \hline
        & 0 static & 1963.07 & 24769.48 & ~~27.19 days \\
        & 1 static & 448.37 & 4316.57 & 119.14 days \\
        & 2 static & 98.07 & 550.44 & ~~~~1.49 years \\
        \hline

        Metaphone &&&& \\
        \hline
        & 0 static & 27138.78 & 529229.35 & ~~~~1.97 days \\
        & 1 static & 2822.74 & 23932.39 & ~~18.91 days \\
        & 2 static & 339.84 & 1730.97 & ~~15.45 days \\
        \hline

@@

As it can be seen metrics like Levenshtein have a low overall average and would require much more attacker resources to become feasible. However, metaphone has attacks that could be computed on average in under 2 days

\section{Distribution of vulnerable keys}
As discussed in the design of the second experiment (See Section \ref{sec:exp2}) the attacks sampled from a list of `vulnerable keys'. These vulnerable keys were created using real keys extracted from PGP key servers. These keys were then randomly sampled and used to create the combined key as discussed in Section \ref{sec:pep}. 100,000 random key pair were as the total sample, and any vulnerable keys for each attack level were recorded.

@@

\begin{table}[!h]
    \centering
    \begin{tabular}{|lll|}
        \hline
        \textbf{Attack Type} & \textbf{Metric} & \textbf{Vulnerable \%} \\
        \hline 
        2 static (152) && \\ 
        & Levenshtein & ~~4.295\% \\
        & Metaphone & 24.095\% \\
        & NYSIIS & 10.441\% \\
        \hline
        1 static (1525) && \\ 
        & Levenshtein & ~~0.827\% \\
        & Metaphone & 15.569\% \\
        & NYSIIS & ~~4.341\% \\
        \hline
        0 static (15250) && \\ 
        & Levenshtein & ~~0.157\% \\
        & Metaphone & 10.202\% \\
        & NYSIIS & ~~1.824\% \\
        \hline
    \end{tabular}
    \caption{Number of vulnerable keys per metric}
\end{table}

\section{Generation of keys}
To demonstrate that the the generation of the near collision keys is not only theoretical actual generation of keys was performed using GreenOnion. A random metric was selected from the three carried forward from the first experiment. Alongside this a random uncontrolled key was generated as the simulated attack target (See Appendix \ref{appendix:uncontrolled_key} for the armor public key). Then for each attack level (0 static, 1 static, 2 static) a key was computed. NYSIIS was chosen as the selected metric. To expedite the process an initial search was performed for controlled keys that had the highest number of near-collision keys, this was due to the demonstration of the actual generation of keys. Producing near-matching keys that have a very small number of potential matches, therefore, adds very little to this demonstration with a large computation cost.

@@

Tables \ref{tab:nysiis0}, \ref{tab:nysiis1} and \ref{tab:nysiis2} contain the parameters and results on the computation. Due to varying availability of resources each computation has a varying hashing speed. This, however, has been normalized by the introduction of the "GPU Day" metric. This is simply the computation time required to reach the same conclusion on a single 2000 MH/s GPU. As it can be seen most notable from Table \ref{tab:nysiis2} the generation of the actual Trustwords differs in only 3 characters making it arguably very similar.

When linking this generated key to results of the second experiment (See Section \ref{sec:exp2}) computation of 2.53 days on a single mid-range GPU is able to achieve around a 28\% success rate when assessed against actual users. Even with the least restricted attack type presented in Table \ref{tab:nysiis0} the computation of half a day can provide almost a 10\% success rate when attacking users. This means any user with a single commodity GPU could compute enough keys in less than a week to have a very high probability of fooling an actual user assuming the success rate is consistent across all keys.

>>>>

\begin{table}[h!]
    \centering
    \begin{tabular}{|l|l|l|}
        \hline
        \textbf{Metric} & \textbf{Average Rating}  & \textbf{$\sigma$}\\
        \hline
        Leven     & 3.66  & 1.15\\
        NYSIIS    & 2.92 & 1.31\\
        Metaphone & 2.56 & 1.32\\
        Phonetic Vec & 2.50 & 1.35\\
        Soundex & 2.08 & 1.12 \\
        \hline
        Random  & 1.16 & 0.46\\
        \hline
    \end{tabular}
    \caption{Average metric performance}
    \label{tab:exp1_results}
\end{table}

@@

\subsection*{Considerations}
As discussed in Section \ref{sec:exp1_considerations} compromises were made in order to fullfil all requirement with a minimized cost. Levenshtein's abnormal performance further backs up concerns around the visual aspect biasing the performance of the metric. This will have to be considered when interpreting the results.

Even with the discussed issues, the aim of the experiment was to promptly reduce the number of metrics for use later in the project. This experiment, therefore, has achieved that goal of providing three metrics for the subsequent experiment while balancing between accuracy and expenditure. The results are also an improvement over informal ad-hoc methods. Further work could aim to reproduce this study with the proposed audio based design.

@@

\section{Experiment 2 - Trustword attacks}
\label{sec:exp2}

Section \ref{sec:exp2_design} explains the design of the experiment. This section will present and discuss the results of the experiment alongside a comparison to relevant literature.

@@

\subsection*{Considerations}
As previously mentioned, the set of recruited participants are more highly educated than the general population. This combined with the low average age contributes to an inevitable bias being introduced into the data. An assumption can be made that higher education leads to more skillful interaction with computer based systems, this, therefore, with the previous assumption in mind means the results of this experiment being a `best case' scenario. The attacks, therefore, would be expected to be more successful on less technical users. This, however, requires further research and possible empirical data to determine the validity of the assumption.

During this study the main task was to perform the authentication ceremony a large number of times. In the real-world the ceremony is a secondary task due to it not strictly being required. This alongside the potential for users to downplay the possibility of attack leads to the conclusion that the success rates could be much higher in a real-world setting. The assumption is that these results display the success rate for extremely attentive user where they will make sure to double check with their authentication partner multiple times. This is opposed to the assumption that the majority of users will aim to complete the task as quickly as possible.

\subsection*{Comparison to alternative literature}
This section will aim to compare the results of the experiment to similar literature.

Work by Kainda \textit{et al.}\cite{kainda2009usability} (previous discussed in Chapter \ref{cha:LiteratureReview}) is the most comparable to this experiment. They were the only study to use exactly 4 words, but differed on the size of dictionary (1024 words) and how a near-match was calculated. Near-matches were a difference in a single word but without the consideration for similarity, this is the unique aspect considered with this experiment.

However, with those aspect in mind attacks on words encoding received an overall success rating of 3.3\%, considerably lower than that of this study. In the worst case our simulated attacks achieved almost 3 times as many successes compared to this study.

Other relevant work by Dechand \textit{el al.}\cite{dechand2016empirical} also discussed in Chapter \ref{cha:LiteratureReview} assess the success rate of attacks on words. This is less similar to the experiment as 14 words per attack were assessed with each participant, where the comparison was performed visually. However, the success for the PGP Word list was 8.78\%. As 10/14 words were kept static more comparable to comparable the results to the highest attack strength ``2 static''. Therefore, there is another 3 fold improvement in the success rates of our simulated attacks.

The final relevant paper to compare is that of Tan \textit{et al.}. This paper had the highest number of words assessed with 16 overall. With it assessing the same wordlist and attack strength as the work by Dechand \textit{et al.}. The attack success was 14\% overall, this again compared to the highest attack assessed in the experiment results in a sizeable difference.

In conclusion, all similar literature had much lower attack success rates that the results presented in this experiment. With all papers using similarly designed words lists it highly suggests that the deficiencies in Trustwords are the cause for the substantial increase in attack success. Alongside this, the consideration for similarity when calculating near-collisions could have also resulted in the higher attack success rates. This aspect is also a unique consideration compared to available literature.

@@

\begin{table}[!h]
    \centering
    \begin{tabular}{|lllll|}
        \hline
        \textbf{Metric} & & \textbf{Mean matches} & \textbf{$\sigma$} & \textbf{Compute Time} \\
        \hline
        NYSIIS &&&& \\
        \hline
        & 0 static & 1963.07 & 24769.48 & ~~27.19 days \\
        & 1 static & 448.37 & 4316.57 & 119.14 days \\
        & 2 static & 98.07 & 550.44 & ~~~~1.49 years \\
        \hline

        Metaphone &&&& \\
        \hline
        & 0 static & 27138.78 & 529229.35 & ~~~~1.97 days \\
        & 1 static & 2822.74 & 23932.39 & ~~18.91 days \\
        & 2 static & 339.84 & 1730.97 & 157.45 days \\
        \hline

@@

As it can be seen metrics like Levenshtein have a low overall average and would require much more attacker resources to become feasible. On the other hand, Metaphone has attacks that could be computed on average in under 2 days. The success rate for this attack type in the second experiment was 11.01\% on average. This means on comity hardware commonly found in the home, an attacker could compute a key in less than two days that could succeed more than 10\% of the time. This is substantial and highlights on weaknesses in the Trustword system.

\section{Distribution of vulnerable keys}
As discussed in the design of the second experiment (See Section \ref{sec:exp2}) the attacks sampled from a list of `vulnerable keys'. These vulnerable keys were created using real keys extracted from PGP key servers. These keys were then randomly sampled and used to create the combined key as discussed in Section \ref{sec:pep}. 100,000 random key pair were created and used as the sample. Any vulnerable keys in this set were recorded and used in the experiment.

@@

\begin{table}[!h]
    \centering
    \begin{tabular}{|lll|}
        \hline
        \textbf{Attack Type} & \textbf{Metric} & \textbf{Vulnerable \%} \\
        \hline 
        2 static (152) && \\ 
        & Levenshtein & ~~4.295\% \\
        & Metaphone & 24.095\% \\
        & NYSIIS & 10.441\% \\
        \hline
        1 static (1525) && \\ 
        & Levenshtein & ~~0.827\% \\
        & Metaphone & 15.569\% \\
        & NYSIIS & ~~4.341\% \\
        \hline
        0 static (15250) && \\ 
        & Levenshtein & ~~0.157\% \\
        & Metaphone & 10.202\% \\
        & NYSIIS & ~~1.824\% \\
        \hline
    \end{tabular}
    \caption{Number of vulnerable keys per metric}
    \label{tab:vulnkeys}
\end{table}

Table \ref{tab:vulnkeys} contains the breakdown of the number of vulnerable keys. The takeaways from this table is the extremely low values for Levenshtein in the higher attacks. This is due to the low number of overall matches produced by Levenshtein. This means Levenshtein will not be effective in the vast majority of cases. However, the standout metric is Metaphone with a good proportion of vulnerable keys, it was the worst performer when assessed against real users but only by as little as 2\%. If you take into consideration the number of vulnerable keys detected in the set alongside the average amount near-collision matches in Table \ref{tab:average_perm} Metaphone appears to be the most usable metric overall.

\section{Generation of keys}
To demonstrate that the the generation of the near collision keys is not only theoretical actual generation of keys was performed using GreenOnion. A random metric was selected from the three carried forward from the first experiment. Alongside this a random uncontrolled key was generated as the simulated attack target (See Appendix \ref{appendix:uncontrolled_key} for the armor public key). Then for each attack level (0 static, 1 static, 2 static) a key was computed. NYSIIS was chosen as the selected metric. To expedite the process an initial search was performed for controlled keys that had the highest number of near-collision keys, this was due to the demonstrative purpose of this experiment. Producing near-matching keys from key pairs with a very small number of potential matches, adds very little to this demonstration.

@@

Tables \ref{tab:nysiis0}, \ref{tab:nysiis1} and \ref{tab:nysiis2} contain the parameters and results on the computation. Due to varying availability of resources each computation has a varying hashing speed. This, however, has been normalized by the introduction of the "GPU Day" metric. This is simply the computation time required to reach the same conclusion on a single 2000 MH/s GPU.

As it can be seen most notable from Table \ref{tab:nysiis2} the generation of the actual Trustwords differs in only 3 characters making it arguably very similar. When linking this generated key to results of the second experiment (See Section \ref{sec:exp2}) computation of 2.53 days on a single mid-range GPU is able to achieve around a 28\% success rate when assessed against actual users. Even with the least restricted attack type presented in Table \ref{tab:nysiis0} the computation of half a day can provide almost a 10\% success rate when attacking users. This means any user with a single commodity GPU could compute enough keys in less than a week to have a very high probability of fooling an actual user.
